\section{Background Research}
\label{sec:background}

A lot of medical data is collected nowadays on a routine basis by clinicians and could play a critical role to support evidence based decision making. However, the process of analysing the data and selecting the "correct" statistical model is often a demanding process for clinicians. A system helping them to select and apply appropriate models on these clinical data sets would empower them -- even with minimal or no statistical knowledge -- to make data driven decisions without the need of applying statistics. 

It has been shown in \cite{sassoon2014}, that a system based on argumentation schemes and a statistical knowledge base could close the gap between the clinician performing analysis and the statistician having the in-depth knowledge of the underlying theory. The relevant theoretical elements will be explained in the following sections.


\subsection{Structure of the Background Research}

The approach for a statistical model selection proposed in \cite{sassoon2014} is based on computational models of argumentation. Usually multiple assumptions have to be fulfilled for statistical models to be applicable on a dataset. These assumptions are defeasible and may lead to multiple possible models, which requires argumentation over assumptions and models to provide a reasonable statistical model selection. An introduction to \glspl{AF} is given in \autoref{sub:dung}. 

Non-monotonic argumentation (as proposed in \cite{liao,dung1995}) and monotonic (classic) logic (as proposed in \cite{Reiter1980}) are in general different approaches to deal with reasoning. However, recent research is focusing on dialogue based approaches which are mostly based on non-monotonic argumentation \cite{parsons2000,Walton1995}. 
Nevertheless Sassoon \textit{et al.} propose to employ preferences by using \glspl{EAF} to reason about the order of applicable models and to deliver a final statistical model which should be used. 

To understand this approach, an extension to the standard framework to reason over preferences is presented later in this chapter (see \autoref{sub:eaf}). Other possible solutions to argue over preferences are explained in \autoref{sub:paf}.

Finally, a summary of Sassoon \textit{et al.} \cite{sassoon2014} on the problem of finding applicable and choosing preferred models by clinicians for a given research question is provided in \autoref{sub:statistical_model_selection}. In our application we focused on the approach described by the most recent papers \cite{sassoon2016,sassoon2016CD} which will be summarised as well.


\input{contents/literatur_general}
\input{contents/literatur_preferences}

A short overview over other approaches to deal with preferences in argumentation frameworks can be found in \autoref{app:other_afs}. 
\input{contents/summary_sassoon}

%%%%%%%%%%%%%%%%%%
%\input{contents/related_clinical_analysis} 
