\subsection{Argumentation Theory: General introduction}

In the following section a general overview on \glspl{AF} will be given. The notation and definitions are based on Dung's theory \cite{dung1995} as it is a widely used definition for argumentation frameworks.
\begin{definition}
	An argumentation framework is a tuple $AF = \langle \S, \R \rangle$ where $\S$ is a set of arguments and $ \R \subseteq \S \times \S$. $\R$ is a binary relation and called attack relation.
\end{definition}


An (abstract) argumentation framework can be represented as a directed graph where nodes are arguments and an arrow from a node $A$ to a node $B$ represents an attack from argument $A$ against $B$.

\begin{exa}
 \autoref{fig:small_af} represents an \gls{AF} with the definition $AF = \langle \{A, B, C, D, E\}, \{(A,B), (B, C), (B, E), (C, B), (D,C), (D,D)\}\rangle$. This framework will be used as an example for the following definitions.
\end{exa}


\begin{figure}[h]
\centering
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2cm,
                    thick]

  \node[main node] (A) {A};
  \node[main node] (B) [right of=A] {B};
  \node[main node] (C) [right of=B] {C};
  \node[main node] (D) [below of=C] {D};
  \node[main node] (E) [below of=B] {E};
  
  \path[every node/.style={font=\sffamily\small}]
    (A) edge node [left] {} (B)
    (B) edge [bend right] node [left] {} (C)
    	edge node [left] {} (E)
    (C) edge [bend right] node [left] {} (B)
    (D) edge node [left] {} (C)
        edge [loop right] node {} (D)
    ;
\end{tikzpicture}
\caption{Small example argumentation framework}
\label{fig:small_af}
\end{figure}


\begin{notation}
In this paper we use capital letters $\{A, B, ...\}$ to denote arguments. $AB$ or $(A, B)$ denotes an attack from $A$ to $B$ ($(A,B) \in \R$).	
\end{notation}

For the following definitions let $AF=\langle \S, \R \rangle, S' \subseteq \S$.

\begin{definition}
	A subset $S'$ is \textbf{conflict-free} iff $ \forall A, B \in S': (A, B) \notin \R$ \textit{(the subset has no attacks between its arguments)}.
\end{definition}
\begin{remark}
	Conflict-free subsets are of interest, as these sets are not directly contradictory. In other words, a conflict-free subset of an argumentation framework does not contain any attacks between its members.
\end{remark}
\begin{exa}
Conflict-free subsets in the provided example are $\emptyset, \{A\}, \{B\}, \{C, E\}, ...$. The sets $\{D\}, \{A, B\}, \{B, C\}$ are not conflict-free.
\end{exa}

\begin{definition}
$A$ is \textbf{acceptable} w.r.t. a subset $S'$ iff  $\forall B \in \S: (B, A) \in \R \Rightarrow \exists C \in S': (C, B) \in \R$ \textit{(an argument $A$ is acceptable with respect to a subset $S'$ iff for each attacker $C$ of $A$ there is an argument in $S'$ that attacks this attacker of $A$). }
\end{definition}

\begin{remark}
If an argument $A$ is acceptable w.r.t. a subset $S'$, then there exists no holding counter-argument in this \gls{AF} causing the argument $A$ not to hold.
\end{remark}

\begin{lemma}
	$S'$ \textbf{defends} $X$, if and only if $X$ is acceptable with respect to $S'$.
\end{lemma}

\begin{exa}
In  \autoref{fig:small_af} $E$ is acceptable with respect to $\{A\}$. $A$ is acceptable with respect to $\emptyset$. 
\end{exa}


\begin{definition}
The \textbf{characteristic function} of an argumentation framework $AF$ (denoted as $F_{AF}$) is defined by the following:
	\begin{align*}
		&F_{AF}: 2^{\S} \rightarrow 2^\S &\\
		&F_{AF}(S') = \{A | A~\text{is acceptable with respect to}~S'\} &
	\end{align*}
\end{definition}
\begin{notation}
	If it is unambiguous, we often refer to $F_{AF}$ with $F$. 
\end{notation}


\begin{definition}
	A conflict-free set $S' \subseteq \S$ is \textbf{admissible} iff $S'$ defends all of its arguments (\textit{each argument in $S'$ is acceptable with respect to $S'$}) or $S' \subseteq F_{AF}(S')$.
\end{definition}

\begin{exa}
In the given example in \autoref{fig:small_af} sets $\{A\}, \{A, E\}$ are admissible, and $\{B\}$ is conflict-free but not admissible, since $B$ is not acceptable with respect to $\{B\}$.
\end{exa}

\begin{definition}
$S'$ is a \textbf{complete extension} iff  $S'$ is admissible and each argument that is acceptable with respect to $S'$ (which is defended by $S'$) belongs to $S'$.
\end{definition}

\begin{remark}
	A complete extension is a set of arguments that defends all members and includes all arguments that can be accepted regarding these members. In \autoref{fig:small_af} the set $S'=\{A\}$ is acceptable, but as this set defends as well $E$ (the only attacker $B$ is not acceptable w.r.t. $S'$), this argument must be included in $S'$ to make the set complete. Hence $S' = \{A, E\}$ is a complete extension. 
\end{remark}


\begin{exa}
$X = \{A, E\}$ is a complete extension in \autoref{fig:small_af}, since it is admissible and it defends $A$ and $E$. Note that $C$ is not defended by $X$ since it does not attack $D$ and $D$ cannot be defended.
Complete extensions in \autoref{fig:pref_af} are $\{A\}, \{A, C\}$ and $\{A, D\}$.
\end{exa}


\begin{definition}
A grounded extension ($GE_{AF}$) of an argumentation framework $AF$ is the minimal (with respect to set inclusion) complete extension of $AF$. In other words $GE_{AF}$ is the least fixed point of $F_{AF}$. ($GE_{AF} = F_{AF}(\emptyset)$).
\end{definition}

\begin{remark}
	The grounded extension can be understand as the set of arguments an rational agent can accept without doubts, as it contains only the minimal acceptable arguments for an argumentation framework and does not require the agent to assume anything about any argument.
\end{remark}

\begin{exa}
	The grounded extension of the example framework in \autoref{fig:small_af} is $\{A, E\}$.
	The grounded extension of the example framework in \autoref{fig:pref_af} is $\{A\}$.
\end{exa}


\begin{definition}
A preferred extension of an argumentation framework $AF$ is a maximised (with respect to set inclusion) admissible set of $AF$.
\end{definition}

\begin{figure}[t]
\centering
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2cm,
                    thick]

  \node[main node] (A) {A};
  \node[main node] (B) [right of=A] {B};
  \node[main node] (C) [right of=B] {C};
  \node[main node] (D) [right of=C] {D};
  \node[main node] (E) [right of=D] {E};
  
  \path[every node/.style={font=\sffamily\small}]
    (A) edge node [left] {} (B)
    (C) edge node [left] {} (B)
    	edge [bend right] node [left] {} (D)
    (D) edge [bend right] node [left] {} (C)
	    edge [] node [left] {} (E)
    (E) edge [loop right] node {} (E)
    ;
\end{tikzpicture}
\caption{Example argumentation framework}
\label{fig:pref_af}
\end{figure}

\begin{exa}
The preferred extensions in \autoref{fig:pref_af} are $\{A, C\}$ and $\{A, D\}$.
\end{exa}

\begin{definition}
A conflict-free set of arguments $S' \subseteq \S$ is called a \textbf{stable extension} iff $S'$ directly attacks each argument which does not belong to $S'$.
\end{definition}
\begin{exa}
The $AF$ in \autoref{fig:pref_af} has the stable extension $\{A, D\}$. $\{A, C\}$ is a preferred, but not a stable extension.
\end{exa}


\begin{remark}
The different extensions of a $AF = \langle \S, \R \rangle$ have the following relations between each other \cite{dung1995}:
\begin{itemize} 
	\item Each preferred extension is as well a complete extension.
	\item Each stable extension is as well a preferred extension.
	\item The grounded extension is the least (with respect to set inclusion) complete extension and therefore unique for each $AF$.
	\item Preferred extensions are the most (with respect to set inclusion) complete extensions.
	\item Arguments accepted in the grounded extension are skeptically accepted in the $AF$.
	\item Every $AF$ has at least one preferred extension.
	\item A stable extension does not always exist.
\end{itemize}
\end{remark}

\begin{definition}
An argument is regarded as \textbf{sceptically accepted under a semantic}, iff it is accepted in all extensions of this semantic (complete, grounded, preferred, stable). An argument is regarded as \textbf{credulously accepted under a semantic}, iff it accepted in at least one, but not all, extensions of this semantic. 	
\end{definition}

\begin{exa}
In \autoref{fig:pref_af} $\{A\}$ is sceptically accepted under each semantic. $\{C, D\}$ are credulously accepted under a preferred semantic. $\{D\}$ is as well accepted sceptically under the stable semantic.
\end{exa}


Furthermore \cite{dung1995} introduces \textit{well-founded argumentation frameworks} (having exactly one extension which is grounded, preferred and stable), \textit{uncontroversial argumentation frameworks} and \textit{coherent argumentation frameworks} (each preferred extension of an $AF$ is stable). Regarding the problem we are looking at, defeasible argumentation is really important, as we are dealing with inconsistent \glspl{SKB}. Hence these restricted argumentation frameworks will not be used in this project, therefore they are not discussed any further.

In extension to the discussed extension-based semantics, \cite{liao} introduces a so called \textit{labelling-based approach} where there are usually three labels: \texttt{IN} (accepted argument), \texttt{OUT} (rejected argument) and \texttt{UNDEC} (undecided whether this argument is accepted or rejected) and a labelling function $\lambda: \S \rightarrow \{IN, OUT, UNDEC\}$.

By defining legally labelled arguments, definitions for \textit{conflict-free labelings},~\textit{admissible labelings} and \textit{complete/grounded/preferred labelings} can be derived. As there exists a bijective projection, they can be easily transferred to the extension-based semantics already introduced in this section.

