\section{Specification}
\label{sec:specification}
\todo{Little bit more specifying the format of inputs and outputs, this should be addressed in a more detailed specification chapter in the eventual report}

In accordance with the selected methodology of Use Cases 2.0 (see \autoref{sec:design}) no in-depth specification has been written, however a reasonable amount of Use Cases have been defined and refined. These were then reviewed by the client and discussed in detail. As mentioned, the project used Trello as management tool. All Use Cases have been described on cards over there and subtasks have been generated out of these Use Cases. In the following section an exemplary description of the different Use Cases and thereby the requirements of the software are presented. They are directly reflected by the description in \cite{sassoon2014,sassoon2016, sassoon2016CD}.

Each \gls{use_case} consists in general of the following attributes:

\begin{itemize}
\item Name
\item Desired outcome
\item (Main-)\glspl{Actor}
\item Flow to achieve the desired outcome
\item Alternative flow (optional)
\end{itemize}


\autoref{tab:usecases} shows an overview over the major \glspl{use_case} that have been generated during the requirements analysis. For the sake of simplicity they have not been integrated into this dissertation. However they are public available on the \href{https://trello.com/b/ywCkicpc}{Trello-Board}.

In addition to the described \glspl{use_case} the following weak requirements influenced the development of the final project:

\begin{itemize}
	\item The system should be designed as an interactive \textbf{web application} to ensure:
	\begin{itemize}
		\item Access for multiple users.
		\item Portability between different operating systems.
		\item No requirement of installation of software on local computers.
		\item Clinician and Statistician can share the same infrastructure without the need of working at the same place.
	\end{itemize}
	\item A decent test suite should be provided to ensure the functionality of the system.
	\item The system must be suitable for different user types (\glspl{Actor}).
	\item The system has to provide different levels of access for different user groups.
	\item The system should be able to execute test scripts as \texttt{R}-Scripts.
	\item The system should be hosted on a free accessible hoster.
\end{itemize}

\begin{landscape}
	\begin{longtable}{ l c p{8cm} l l p{3cm} }
		\textbf{Reference}                         & \textbf{\gls{Actor}}\footnote{C: Clinician, S: Statistician, A: Admin} &\textbf{Description} &  \textbf{RC} & \textbf{MuSCoW} &  \textbf{Comments}\\
		\href{https://trello.com/c/KEOokZp9}{UC1}   & 	- & 	Enter two default models into the system as code without user interface including definition of assumptions & RC1 & Must &  For initial testing purposes  \\
		\href{https://trello.com/c/ebVrFdA5}{UC2}   & 	C & 	Get models that are appropriated for a research question & RC1	& Must &	   \\
		\href{https://trello.com/c/ORRBjISQ}{UC2-1} & 	C & 	Store done analysis & RC2 & Should &  see \autoref{as:1} \\
		\href{https://trello.com/c/qKLAoWRj}{UC3} 	&  	S & 	Define static critical \& non-critical assumptions for models & - & - & obsolet \\
		\href{https://trello.com/c/7NINsfz8}{UC4}   & 	C & 	Check that a dataset meets the set of assumptions of a model and that the queries to the clinician regarding the research question's  assumptions are met as well. & RC1 & Must   &   \\
		\href{https://trello.com/c/22JGne3r}{UC5}   & 	C & 	Select a research question & RC1 & Must &   \\
		\href{https://trello.com/c/CVGBVWID}{UC6}   &   C, S, A & 	Login into the system and be authenticated with your role & RC2 & Should &	 \\
		\href{https://trello.com/c/pId27kJM}{UC6-1} &   A & 	Create new users & RC2 & Must &	 \\
		\href{https://trello.com/c/pQ98qgSL}{UC6-2} &  	A & 	Delete users & RC2 & Must	 &   \\
		\href{https://trello.com/c/mvxBeNSR}{UC6-3} &  	A & 	Modify users & RC2 & Should &   \\
		\href{https://trello.com/c/DidVQKAS}{UC7}   &   C & 	Fill patient data into the system to be checked by the models & RC2 & Must &  \\
		\href{https://trello.com/c/be2088JH}{UC8}	& 	C & 	See arguments for and agains models for a research question & RC2 & Must &   \\
		\href{https://trello.com/c/Ca9mA3uA}{UC9}   &   S & 	Add a new Model Preference Mode & RC3 & Must &   \\
		\href{https://trello.com/c/1s656fA9}{UC10}  &   C & 	Get recommended model taking into account global preferences (by using AS2) & RC3 & Should & 	 \\
		\href{https://trello.com/c/xUDStSOK}{UC11}  &   A & 	Create new users with a specific role for the system & RC3 & Could &    \\
		\href{https://trello.com/c/5UMo7o6U}{UC12}  &   S & 	Enter additional analysis models into the system in a defined language as text so that it will be regarded as an option for applicable models	& RC3 & Should & \\
		\href{https://trello.com/c/2V6Cl65u}{UC12-1}&   S & 	Add Test-Argument into the system & RC2 & Must & \\
		\href{https://trello.com/c/OwM2Z7wt}{UC12-2}&   S & 	Add Query-Argument into the system & RC2 & Must &  \\
		\href{https://trello.com/c/VThxB5aS}{UC12-3}&   S & 	Add Test-Query-Assumptions into the system & RC4 & Should & added during the project\\
		\href{https://trello.com/c/CkpJUNPW}{UC12-4}&   S & 	Run Test-Argument on a specific existing dataset & RC3	& Should &  \\
		\href{https://trello.com/c/Rg6GPnNE}{UC12-5}&   S & 	Add Blank Arguments for grouping of assumptions & RC2 & Could & \\
		\href{https://trello.com/c/ORlMByiQ}{UC13}  &   S & 	Get in-depth information about algorithmic performance and steps it proceeds & RC4 & Would & Rejected, as not required.\\
		\href{https://trello.com/c/NcV3lo4w}{UC14}  &   C & 	Enter personal preferences for statistical models and/or analysis techniques & RC4 & Could &   \\
		\href{https://trello.com/c/BOUu2hKN}{UC15}  &   C & 	See argumentation frameworks that are generated for/agains the statistical models. Graph Export: See arguments for and agains models for a research question in a nice and graphical &RC4 & Would & 	 The export to PDF has been ignored, as the user can just print the generated graphs.  \\
		\href{https://trello.com/c/3FCcFdmm}{UC16}  &   C & 	See analysis process of argumentation framework as visualisation & RC4 & Would	&    \\
		\href{https://trello.com/c/Hv2xe2UW}{UC17}  &   S & 	Enter additional research questions into the system & RC3 &Could& \\
		\href{https://trello.com/c/w1YiIgU7}{UC17-1}&   S & 	Modify research questions&RC3 & Must &  \\
		\href{https://trello.com/c/UbT5mtDx}{UC17-2}&   S & 	Delete research questions&RC3&Must& \\
		\href{https://trello.com/c/dpLHOxbB}{UC18}  &   S & 	Include R Script execution	 & RC1 & Must & \\
		\href{https://trello.com/c/bZHdWpkt}{UC19}  &   S & 	Enter global preferences for statistical models and/or analysis techniques& RC3 & Could &	 \\

		\caption{List of the different use cases that have been evaluated during the requirements analysis.}	
		\label{tab:usecases}
	\end{longtable}
\end{landscape}

The \glspl{use_case} defined in \autoref{tab:usecases} where then further defined, requirements deriving from it have been generated as new cards (\glspl{use_case_slices})



